Complementary roles of Theta and Alpha in Multi-Item Associations

### 2019-06-12 manuscript.tex
small changes from Tims comments

\section*{Acknowledgements}\label{sec:acknowledge}

@@

These results provide another data point in the Dependent Events paradigm, and helps illustrate the temporal dynamics that was not previously possible in the fMRI studies.  Specifically, the response locked theta effects and stimulus locked alpha effects both support the mechanism proposed by the computational model, and provide extra insight into the dynamics support the Dependent Events paradigm.

>>>>

%\section*{Acknowledgements}\label{sec:acknowledge}

@@

These results provide new insight into the Dependent Events paradigm, and helps illustrate the temporal dynamics that was not previously possible in the fMRI studies.  Specifically, the response locked theta effects and stimulus locked alpha effects both support the mechanism proposed by the computational model, and provide extra insight into the dynamics support the Dependent Events paradigm.
